\vspace*{-40pt}Numerical Eigenvalue Algorithms

### 2025-03-07 documents/paper.tex
back to pdflatex
finish presentation

\usepackage{enumitem}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{graphicx, float}
\usepackage[style=alphabetic]{biblatex}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{titling}
\usepackage{vwcol}
\usepackage{setspace}
\usepackage{empheq}
\usepackage{tabularray}
\usepackage{cancel}
\usepackage{esdiff}
\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{mdframed}
\usepackage{esdiff}
\usepackage{tikzsymbols}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{varwidth}
\usepackage{parskip}
\usepackage{pgfplots}
\usepackage{soul}
\usepackage{tcolorbox}
\usepackage{fontspec}

@@

\begin{tcolorbox}[title={Hessenberg matrix},colback=blue!5!white,colframe=blue!75!black,parbox=false]
	A Hessenberg matrix $H$ is one that is ``almost'' triangular: it is a triangular matrix with nonzero entries in the diagonal just above or just below its main diagonal. A \textbf{lower} Hessenberg matrix $H$ satisfies $H_{ij}=0$ for all $j>i+1$, and an \textbf{upper} Hessenberg matrix $H$ satisfies $H_{ij}=0$ for all $i>j+1$.

@@

Next, a comparison of the time taken. The Power Method is so drastically different from the $QR$ Algorithms we will only compare the Basic and Improved Algorithms. Since the Francis double-step algorithm is too complicated, we will modify (``un-improve'') the Improved Algorithm by performing a Hessenberg reduction, then applying the Basic $QR$ Algorithm to the Hessenberg matrix.

We will perform the following procedure for a constant $m$ number of iterations:
\begin{enumerate}
	\item Set $A$ to some random $n\times n$ matrix.
	\item Calculate the time to run $m$ iterations of the Basic $QR$ Algorithm on $A$.
	\item Calculate the time to calculate the Hessenberg matrix $H$ from $A$, and to run $m$ iterations of the Basic $QR$ Algorithm on $H$.
	\item Repeat steps 2 and 3 some number of times, then take the average of each elapsed time.
	\item Increment $n$ by some amount, then start back from step 1.
\end{enumerate}

>>>>

\usepackage{enumitem}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{graphicx, float}
\usepackage[style=alphabetic]{biblatex}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{titling}
\usepackage{vwcol}
\usepackage{setspace}
\usepackage{empheq}
\usepackage{tabularray}
\usepackage{cancel}
\usepackage{esdiff}
\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{mdframed}
\usepackage{esdiff}
\usepackage{tikzsymbols}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{varwidth}
\usepackage{parskip}
\usepackage{pgfplots}
\usepackage{soul}
\usepackage{tcolorbox}
\usepackage{mlmodern}

@@

\begin{tcolorbox}[title={Hessenberg matrix},colback=blue!5!white,colframe=blue!75!black,parbox=false]
	A Hessenberg matrix is a matrix with nonzero entries only in the diagonal just above or just below its main diagonal. A \textbf{lower} Hessenberg matrix $H$ satisfies $H_{ij}=0$ for all $j>i+1$, and an \textbf{upper} Hessenberg matrix $H$ satisfies $H_{ij}=0$ for all $i>j+1$.

@@

Next, a comparison of the time taken. The Power Method is so drastically different from the $QR$ Algorithms we will only compare the Basic and Improved Algorithms. Since the Francis double-step algorithm is too complicated, we will modify (``un-improve'') the Improved Algorithm by performing a Hessenberg reduction, then applying the Basic $QR$ Algorithm to the Hessenberg matrix. We perform the following for a constant $m$ number of iterations:
\begin{enumerate}
	\item Set $A$ to some random $n\times n$ matrix.
	\item Calculate the time to run $m$ iterations of the Basic $QR$ Algorithm on $A$.
	\item Calculate the time to calculate the Hessenberg matrix $H$ from $A$, and to run $m$ iterations of the Basic $QR$ Algorithm on $H$.
	\item Repeat steps 2 and 3 some number of times, then take the average of each elapsed time.
	\item Increment $n$ by some amount, then start back from step 1.
\end{enumerate}
